Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-03-31 ms.qmd
Added stats for adult / jeuvenile comparison

# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
    # Marine 
        m_adult <- pred[2,] - pred[3,] # Posterior contrast between acclimation and acute effects for adult, marine species
        m_jeuv <-  pred[4,] - pred[1,] # Posterior contrast between acclimation and acute effects for j, marine species
    # Freshwater
        f_ad <- 4
        f_adult <- pred[2+f_ad,] - pred[3+f_ad,] # Posterior contrast between acclimation and acute effects for adult, freshwater species
        f_jeuv <-  pred[4+f_ad,] - pred[1+f_ad,] # Posterior contrast between acclimation and acute effects for j, freshwater species
    # terrestrial
        t_ad <- 8
        t_adult <- pred[2+t_ad,] - pred[3+t_ad,] # Posterior contrast between acclimation and acute effects for adult, terrestrial species
        t_jeuv <-  pred[4+t_ad,] - pred[1+t_ad,] # Posterior contrast between acclimation and acute effects for j, terrestrial species

# Now, lets calculate the contrasts between acute a and j as well as acclim a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
    # Marine 
         m_acute <-  pred[1,] - pred[3,] 
        m_acclim <-  pred[4,] - pred[2,] 
    # Freshwater
            f_ad <- 4
        f_acute <- pred[1+f_ad,] - pred[3+f_ad,] 
        f_acclim <-  pred[4+f_ad,] - pred[2+f_ad,] 
    # terrestrial
        t_ad <- 8
        t_acute <- pred[1+t_ad,] - pred[3+t_ad,] 
        t_acclim <-  pred[4+t_ad,] - pred[2+t_ad,]

# Now lets do a quick. Note that I fixed up some design matrix issues which made acclim the ref level, which was wrong
#  mod_results(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num",  by = "life.hist", data = lnRRQ10_data)
#  newdata %>% arrange(habitat, life.hist, type) %>% filter(habitat == "t")

@@

Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%). Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B). While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2). Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3).

>>>>

# Now, lets calculate the contrasts between acute and acclim for a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
    # Marine 
        m_adult <- pred[2,] - pred[3,] # Posterior contrast between acclimation and acute effects for adult, marine species
        m_jeuv <-  pred[4,] - pred[1,] # Posterior contrast between acclimation and acute effects for j, marine species
    # Freshwater
        f_ad <- 4
        f_adult <- pred[2+f_ad,] - pred[3+f_ad,] # Posterior contrast between acclimation and acute effects for adult, freshwater species
        f_jeuv <-  pred[4+f_ad,] - pred[1+f_ad,] # Posterior contrast between acclimation and acute effects for j, freshwater species
    # Terrestrial
        t_ad <- 8
        t_adult <- pred[2+t_ad,] - pred[3+t_ad,] # Posterior contrast between acclimation and acute effects for adult, terrestrial species
        t_jeuv <-  pred[4+t_ad,] - pred[1+t_ad,] # Posterior contrast between acclimation and acute effects for j, terrestrial species

# Now, lets calculate the contrasts between acute a and j as well as acclim a and j within each habitat. We need to use pred for that because it's the entire posterior distribution
    # Marine 
         m_acute <-  pred[1,] - pred[3,] # Contrasts acute a and acute j values for marine species
        m_acclim <-  pred[4,] - pred[2,] # Contrasts acclim a and acute j values for marine species
    # Freshwater
            f_ad <- 4
        f_acute <- pred[1+f_ad,] - pred[3+f_ad,] # Contrasts acute a and acute j values for freshwater species
        f_acclim <-  pred[4+f_ad,] - pred[2+f_ad,] # Contrasts acclim a and acute j values for freshwater species
    # Terrestrial
        t_ad <- 8
        t_acute <- pred[1+t_ad,] - pred[3+t_ad,] # Contrasts acute a and acute j values for terrestrial species
        t_acclim <-  pred[4+t_ad,] - pred[2+t_ad,]  # Contrasts acclim a and acute j values for terrestrial species

  # Acute differences between a and j across all habitats
    acute_all <- c(m_acute, f_acute, t_acute); mean(acute_all); quantile(acute_all, c(0.025, 0.975)); pmcmc(acute_all)
    acclim_all <- c(m_acclim, f_acclim, t_acclim)

# Now lets do a quick. Note that I fixed up some design matrix issues which made acclim the ref level, which was wrong. These two lines of code should roughly match
#  mod_results(model1.4, mod = "type", at = list(c_accl_time = 0, habitat = "t"), group = "record_num",  by = "life.hist", data = lnRRQ10_data)
#  newdata %>% arrange(habitat, life.hist, type) %>% filter(habitat == "t")

@@

Overall, $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ differed by only `r mean(avg_change)`% across all habitats (95%CI: `r quantile(avg_change, c(0.025, 0.975))[1]` to `r quantile(avg_change, c(0.025, 0.975))[2]`%). Ectotherms in marine and freshwater environments showed partial compensation of physiological rates (@fig-1 B) amounting to reduced $lnRR_{Q_{10}}_{acclimation}$ of `r mean(change_f)`% (95% CI: `r quantile(change_f, c(0.025, 0.975))[1]` to `r quantile(change_f, c(0.025, 0.975))[2]`) in freshwater and `r mean(change_m)`% (95% CI: `r quantile(change_m, c(0.025, 0.975))[1]` to `r quantile(change_m, c(0.025, 0.975))[2]`) in marine environments. In contrast, terrestrial ectotherms showed no acclimation (possibly even inverse acclimation) -- showing a `r mean(change_t)`% increase in $lnRR_{Q_{10}}_{acclimation}$ (95% CI: `r quantile(change_t, c(0.025, 0.975))[1]` to `r quantile(change_t, c(0.025, 0.975))[2]`, [@fig-1]B). While different trait categories showed different accclimation responses across habitat types, overall, they mirrored patterns seen overall (@fig-2). Acclimation capacity did not vary by life-stage given that there were no differences between $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ between adult and jeuveniles (@fig-3) (Adult-Jeuvenile (Acute): `r mean(acute_all)`, 95% CI: `r quantile(acute_all, 0.025)[1]` to `r quantile(acute_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acute_all)`; Adult-Jeuvenile (Acclimation): `r mean(acclim_all)`, 95% CI: `r quantile(acclim_all, 0.025)[1]` to `r quantile(acclim_all, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(acclim_all)`).
